\documentclass[letterpaper,11pt]{article}

%-------------------------  Package Imports -------------------------%
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%-------------------------  Page Styles -------------------------%
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%-------------------------  Margin Adjustments -------------------------%
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

%-------------------------  Alignment commands -------------------------%
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-------------------------  Sections Formating -------------------------%
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------  ATS Readable -------------------------%
\pdfgentounicode=1

%-------------------------  Custom commands -------------------------%

    \newcommand{\resumeItem}[1]{
      \item\small{
        {#1 \vspace{-2pt}}
      }
    }
    
    \newcommand{\resumeSubheading}[4]{
      \vspace{-2pt}\item
        \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
          \textbf{#1} & #2 \\
          \textit{\small#3} & \textit{\small #4} \\
        \end{tabular*}\vspace{-7pt}
    }
    
    \newcommand{\resumeSubSubheading}[2]{
        \item
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
          \textit{\small#1} & \textit{\small #2} \\
        \end{tabular*}\vspace{-7pt}
    }
    
    \newcommand{\resumeProjectHeading}[2]{
        \item
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
          \small#1 & #2 \\
        \end{tabular*}\vspace{-7pt}
    }
    
    \newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
    
    \renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
    
    \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
    \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
    \newcommand{\resumeItemListStart}{\begin{itemize}}
    \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------  Custom commands -------------------------%

%-------------------------  RESUME STARTS HERE -------------------------%
\begin{document}

\begin{center}
	\textbf{\Huge \scshape Santiago Quintana Moreno} \\ \vspace{1pt}
	\small +52 5538890890 $|$ \href{mailto:santy.10qm.gm@gmail.com}{\underline{santy.10qm.gm@gmail.com}} $|$
	\href{https://github.com/SantiQ0905}{\underline{GitHub: SantiQ0905}} $|$
        \href{https://www.linkedin.com/in/santiago-quintana-moreno-861115192/}{\underline{LinkedIn: Santiago Quintana Moreno}} $|$
        \href{https://www.santiagoquintanamoreno.com/}{\underline{https://www.santiagoquintanamoreno.com/}} 
 
\end{center}


%-----------EDUCATION-----------%
\section{Education}
\begin{comment}
\resumeSubHeadingListStart
\resumeSubheading
{M체nchner Volkshochschule}{M체nchen, Bavaria, Germany}
{German Advanced Language and Skills.}{January 2023 -- March 2023}
\resumeSubHeadingListEnd
\end{comment}

\resumeSubHeadingListStart
\resumeSubheading
{Tecnologico de Monterrey}{Monterrey, Nuevo Leon, Mexico} 
{Computer Technology Engineering (Computer Science) GPA: 3.4 (Nov. 2024)
}{August 2023 -- June 2027}
\resumeSubHeadingListEnd
%-----------EDUCATION-----------%

%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Robotics Mentor}{May 2022 -- Present}
{PrepaTec Overture 7421, 23550, 23619, 26381}{Monterrey, Mexico}
\resumeItemListStart
\resumeItem{Instructed up to 30+ students in wiring, electrical, C++, Java, Python, and WPILib, enabling advanced competition robot programming for seamless hardware-software integration.}
\resumeItem{Educated up to 15+ students on data gathering, analysis and data-driven descicion making through in-house scouting app development. Resulting in the Regional Winning Alliance in Monterrey Regional and Kansas Heartland Regional winners, as well as advancing up to semifinals in the World Championship in Houston.}
\resumeItem{Guide team collaboration across three seasons, streamlining tasks and resources for prompt, efficient competition robot programming and electrical wiring. Provided leadership for 100+ students and mentorship during events, cultivating strategic decision-making, teamwork, and adaptability.}
\resumeItem{Nominated to Wodie Flowers Mentorship award in the Monterrey Regional presented by PrepaTec in 2024.}
\resumeItem{Across three seasons, I contributed as a mentor to a 63.6\% win rate, with a total of 119 won matches and three regional wins.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Overftclib} $|$ \emph{Java, Android, Gradle, Maven}}{2024 - Present}
\resumeItemListStart
\resumeItem{Created and published the Overftclib a comprehensive library designed to modernize programming for FTC robotics competitions and facilitate a seamless transition to FRC-level programming.}
\resumeItem{Developed features for motor control such as PID, Feedforward and Slew Rate to enhance motor control and allow for precise better movements and better performance in Autonomous operation.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{FTC Webots Simulator} $|$ \emph{Java, Webots, Maven, Gradle}}{2024 - Present}
\resumeItemListStart
\resumeItem{Developed and implemented a robotics simulation environment using Webots, tailored for FTC teams to conduct realistic testing and debugging without physical hardware.}
\resumeItem{Allow seeamless integration with Overftclib allowing teams to work with the same code as for the real robot.}
\resumeItem{Focused on integrating sensor accuracy and motor control within the simulator, allowing teams to refine autonomous routines and troubleshoot software in a controlled setting.}
\resumeItemListEnd

\begin{comment}
\resumeProjectHeading
{\textbf{ECOCYCLE, Sponsored by Javer} $|$ \emph{CAD, Python, Arduino, Github, Notion}}{2024 - Present}
\resumeItemListStart
\resumeItem{We developed a sustainable plastic shredder and extruder to process recycled plastic.}
\resumeItem{My role as electrical and software project lead has enabeled the team to complete 35\% of the plastic shredder and 20\% of the extruder. With 100\% of the electronics sourced and tested.} 
\resumeItemListEnd
\end{comment}

\resumeSubHeadingListEnd

%-----------Significant Achievements and Certifications-----------%
\section{Significant Achievements and Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
                        \textbf{Goethe-Zertifikat B2}{: Three Month Certification in Advanced language skills and German Certification B2. 2023} \\
		            \textbf{Advanced Excel}{: Six-week Certification in Advanced Excel by Macquarie University. 2023} \\
		            \textbf{Human-Centered Artificial Intelligence}{: Two-week Certification on Machine Learning, algorithms, Artificial Neural Networks by Tecnol처gico de Monterrey. 2024} \\
                        \textbf{Deep Learning for business}{: Two-week Certification in Deep Learning for business. 2024} \\
		            \textbf{MLH HackMtY 2024}{: Participated in Latin America's largest Hackathon, with a successful result.} \\
                        \textbf{Outstanding Trajectory 2024}{: Recognized as the 1\% of students with an outstanding trajectory by the School of engineering and science from Tecnol처gico de Monterrey.} \\
		      }}
\end{itemize}
%-----------Significant Achievements and Certifications-----------%

%-----------Technical Skills-----------%
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		            \textbf{Programming Languages}{: Java, Python, C/C++, LaTeX} \\
		            \textbf{Developer Tools}{: Git, Github, VS Code, Arduino IDE, Android Studio,
                                JetBrains IDE, Jupyter, MatLab} \\
		            \textbf{Libraries}{: NumPy, Matplotlib, mpltoolkits, mplot3d, Axes3D, WPILib, FTCLib, RoadRunner} \\
                        \textbf{General Software}{: Microsoft Office, GSuite, Notion, Slack} \\
		            \textbf{Languages}{: Spanish (Native), English (C1), German (B2)} \\
		      }}
\end{itemize}
%-----------Technical Skills-----------%

%-----------Social Skills-----------%
\section{Social Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
                        \textbf{Social Skills}{: Adaptability, Effective Communication, Decision-Making, Problem-Solving, Teamwork} \\
		      }}
\end{itemize}
%-----------Technical Skills-----------%

\end{document}